Extended Data

### 2021-04-28 doc/manuscript/Dow_manuscript_Nature.Rmd
writing- results

**The patterns observed at our focual sites were mirrored across an additional `r n_chronologies-n_chronologies_SCBI-n_chronologies_HF` chronologies from `r n_cores_sites-2` (`r EDF_map`).** 
In total, our analysis included # species at sites distributed from XXX to XXX and spanning a ## degree range in April T.** 
*(describe results across all sites)*
(Fig. `r tree_rings`)

>>>>

**The patterns observed at our focual sites were mirrored across an additional `r n_chronologies-n_chronologies_SCBI-n_chronologies_HF` chronologies from `r n_cores_sites-2` (Fig. `r tree_rings`; `r EDF_map`).** 
In total, our analysis included # species at sites distributed from XXX to XXX and spanning a ## $^\circ$C range in April T.
Across all chronologies (focal sites included), RWI was significantly positively correlated with April $T_{max}$ for only #% of records: # of # ring-porous and # or # diffuse-porous species-site combinations.
In contrast, RWI was frequently significantly negatively correlated with $T_{max}$ during peak growing season months (May-August), with significant correlations for #% and #% of species-site-month combinations for ring-porous and diffuse-porous species, respectively.
